Individual heterogeneity in the functional network topography of the medial prefrontal cortex

### 2019-05-17 Manuscript.Rmd
added meta-analysis results file so that they work with manuscript.rmd

# Permutation analysis
# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
# Load the coordinates as studies in a list, because for the contrast the studies are permuted
# Use table(unlist(list)) to get the counts in that case
setwd('./POS')
templist <- dir()
studyList_sv <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())

setwd('../DN/')
templist <- dir()
studyList_DN <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())

>>>>

# Permutation analysis
# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
# Load the coordinates as studies in a list, because for the contrast the studies are permuted
# Use table(unlist(list)) to get the counts in that case
setwd('./metaresultsPOS')
templist <- dir()
studyList_sv <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())

setwd('../metaresultsDN/')
templist <- dir()
studyList_DN <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())
